abxD01 Paper

### 2015-03-03 PAPER.Rmd
Merge Fig 5ab

![**Figure 5A.**](Figure5/figure5a_9x9.png)

![**Figure 5B.**](Figure5/figure5b_6x4.5.png)

@@

# dose <- all[1:99,cols]
# titr <- all[100:153,cols]
# del <- all[154:179, cols]
# toptit <- all[1:153,cols]
# titdel <- all[c(100:153, 154:179),cols]
# topdel <- all[c(1:99, 154:179),cols]
toptitdel <- all[,cols]
library(randomForest)

toptitdel.rf <- randomForest(nextDayCFU ~ ., 
                           data = toptitdel[,-1],  outscale=TRUE,
                           importance=TRUE, proximity=TRUE,
                           keep.forest=TRUE, ntree=5000
)
print(toptitdel.rf)
plot(toptitdel.rf)
varImpPlot(toptitdel.rf, type=1)
imp<-importance(toptitdel.rf)
imp1<-imp[order(imp[,1], decreasing = TRUE),]
#imp2<-imp[order(imp[,2], decreasing = TRUE),]
topimp <- imp1[1:15,]
#toppurity <- imp2[1:15,]
#write.table(topimp, file="~/Desktop/mothur/abxD01/rf/rf.toptitdel.1p.importance.txt", sep="\t", row.names=TRUE)
#write.table(toppurity, file="~/Desktop/mothur/abxD01/rf/rf.toptitdel.1p.importanceNode.txt", sep="\t", row.names=TRUE)
```

@@

par(mfrow=c(1, 1)) 
par(mar=c(5, 5, 4, 2) +0.1, mgp=c(3, 1, 0), las=1) #default is 5.1 4.1 4.1 2.1, bot/left/top/right, also default mgp is c(3,1,0)
plot(results[results[,1]=="control",2], 
     results[results[,1]=="control",3], 
     main="", 
     ylab=expression(paste("Predicted Log ", italic("C. difficile"), " CFU/g Feces")), 
     xlab=expression(paste("Actual Log ", italic("C. difficile"), " CFU/g Feces")), 
     ylim=c(0,9), xlim=c(0,9), xaxt='n', yaxt='n', cex=1.5)
#mtext(bquote("r"^"2" ~ " = " ~ .(signif(rsq, 3))), side=3, line=0)
abline(a=0, b=1, lty="dashed", lwd=2, col="black")
axis(1, at = c(0:9), labels=c(0:9))
axis(2, at = c(0:9), labels=c(0:9))

for(i in 2:(length(legend.labels))){
  points(results[results[,1]==names(legend.labels)[i],2], 
         results[results[,1]==names(legend.labels)[i],3], 
         col=colors[i], pch=pch[i], cex=1.5)
}
legend(x=7, y=3, legend=legend.labels, pch=pch, col=colors, pt.cex=1,  cex=.6, bty="n")

@@

```{r, eval=FALSE}
topimp<-topimp[order(topimp[,1], decreasing=FALSE),]
ids <- read.csv(file = "~/Documents/Github/abxD01/Figure5/rf.toptitdel.1p.importance.ids.csv", header = TRUE)
labels<- paste0(ids$name, " (", ids$otuname, ")")
par(mfrow=c(1, 1)) #+1 to give extra labeling space
par(mar=c(5, 15, 0.5, 2) +0.1, mgp=c(3, 1, 0)) #default is 5.1 4.1 4.1 2.1, bot/left/top/right, also default mgp is c(3,1,0)
plot(topimp[,1], 1:15, xlab="% Increase in Mean Squared Error", yaxt="n", ylab="", pch=16, cex=1.5, xlim=c(20, 80))
axis(2, at = c(1:15), labels = labels, las=1, cex.axis=.9 )
abline(h=c(1:15), lty="dashed", col='black')
```

>>>>

![**Figure 5AB.**](Figure5/figure5ab.png)

@@

toptitdel <- all[,cols]
library(randomForest)

toptitdel.rf <- randomForest(nextDayCFU ~ ., 
                           data = toptitdel[,-1],  outscale=TRUE,
                           importance=TRUE, proximity=TRUE,
                           keep.forest=TRUE, ntree=5000
)
print(toptitdel.rf)
plot(toptitdel.rf)
varImpPlot(toptitdel.rf, type=1)
imp<-importance(toptitdel.rf)
imp1<-imp[order(imp[,1], decreasing = TRUE),]
topimp <- imp1[1:15,]
#write.table(topimp, file="~/Desktop/mothur/abxD01/rf/rf.toptitdel.1p.importance.txt", sep="\t", row.names=TRUE)

@@

#par(mfrow=c(1,2))
design<-as.matrix(1:2)
design<-cbind(design, c(3,3))
layout(design, widths=c(1,1), heights=c(.3, 1))

plot.new()
par(mar=c(rep(0.5, 4)))
legend("bottom", legend=legend.labels, pch=pch, col=colors, pt.cex=1,  cex=1, bty="n", ncol = 2)

par(mar=c(5, 5, 0.5, 0.5) +0.1, mgp=c(3, 1, 0), las=1) #default is 5.1 4.1 4.1 2.1, bot/left/top/right, also default mgp is c(3,1,0)
plot(results[results[,1]=="control",2], 
     results[results[,1]=="control",3], 
     main="", 
     ylab=expression(paste("Predicted Log ", italic("C. difficile"), " CFU/g Feces")), 
     xlab=expression(paste("Actual Log ", italic("C. difficile"), " CFU/g Feces")), 
     ylim=c(0,9), xlim=c(0,9), xaxt='n', yaxt='n', cex=1.5)
#mtext(bquote("r"^"2" ~ " = " ~ .(signif(rsq, 3))), side=3, line=0)
abline(a=0, b=1, lty="dashed", lwd=2, col="black")
axis(1, at = c(0:9), labels=c(0:9))
axis(2, at = c(0:9), labels=c(0:9))

for(i in 2:(length(legend.labels))){
  points(results[results[,1]==names(legend.labels)[i],2], 
         results[results[,1]==names(legend.labels)[i],3], 
         col=colors[i], pch=pch[i], cex=1.5)
}

@@

```{r, eval=FALSE}
topimp<-topimp[order(topimp[,1], decreasing=FALSE),]
ids <- read.csv(file = "~/Documents/Github/abxD01/Figure5/rf.toptitdel.1p.importance.ids.csv", header = TRUE)
#par(mfrow=c(1, 1)) #+1 to give extra labeling space
par(mar=c(5, 15, 0.5, 1) +0.1, mgp=c(3, 1, 0), las=0) #default is 5.1 4.1 4.1 2.1, bot/left/top/right, also default mgp is c(3,1,0)
plot(topimp[,1], 1:15, xlab="% Increase in Mean Squared Error", yaxt="n", ylab="", pch=16, cex=1.5, xlim=c(20, 80))
axis(2, at = c(1:15), labels = rep("", 15), las=1, cex.axis=.9 )
for(z in 1:(dim(ids)[1])){
  name<-as.character(ids$name[z])
  otuname<- as.character(ids$otuname[z])
  mtext(text = bquote(italic(.(name))*" ("*.(otuname)*")"), at=z, side = 2, line = 1, las=2)
}
abline(h=c(1:15), lty="dashed", col='black')
